Incentivizing Exploration by Heterogeneous Users

### 2018-02-05 result_discussion.tex
changes to COLT
significant edits to algorithm section

\section{Problem Setup and Overview of Results}
\dkcomment{I envision this section doing the following:
\begin{enumerate}
\item State the main theorem(s) formally.
\item Discuss lower bounds or impossibility results.
\item Discuss extensions.
\item Discuss the justification or comparison to standard bandits.
\item Discuss the comparison in the 2x2 square.
\end{enumerate}
}

@@

\begin{theorem} \label{thm:main-intro}
Under some technical assumptions, 
there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
\dkcomment{Omitting the density here.}
\end{theorem}

>>>>

\section{Overview of Results and Discussion}
\dkcomment{I envision this section doing the following:
\begin{enumerate}
\item State the main theorem(s) formally.
\item Discuss lower bounds or impossibility results.
\item Discuss extensions.
\item Discuss the justification or comparison to standard bandits.
\item Discuss the comparison in the 2x2 square.
\end{enumerate}
}

@@

\dkcomment{In the results discussion clarify which results need to
  know $T$ and which don't.}

\begin{theorem} \label{thm:main-overview}
Under some technical assumptions, 
there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
\dkcomment{Omitting the density here.}
\end{theorem}
